---
title: "Report on the Nutrition of Starbucks Drinks"
author: "Anton Ngan"
output:
    flexdashboard::flex_dashboard:
        vertical_layout: scroll
        orientation: rows
        source_code: embed
        theme: 
          version: 4
          bootswatch: simplex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE
  )
library(flexdashboard)
library(tidyverse)
library(ggplot2)
library(naniar)
library(plotly)
library(knitr)
library(kableExtra)
library(broom)
library(psych)
library(scales)
```

















Introduction
===================================== 



Row 
------------------------------------

### **Introduction**

The [dataset][datasetsource] has been provided as part of the TidyTuesday weekly 
social data project where the objective is to make learning to work with data 
easier, by providing real-world datasets.  

In the past decade or so, there has been a surge in the popularity of bubble tea, 
smoothies and coffee drinks across Australia. We see that brands like Gonga Cha, 
Chatime, Boost and Starbucks are starting to pop up everywhere we go. Wherever 
we go, there is always a long queue of people waiting to order their drinks and 
a crowd ready to receive their drinks. 

Although, have you ever wondered how healthy the drinks really are? Sometimes, 
these brands offer healthier alternatives or options to decrease the amount of 
sugar in your drinks. This means there are lower calories, reduced sugar, high 
fiber and less carbohydrates in you drinks. So the question to ask now is how 
healthy are the drinks offered by these brands? What nutritional components
do they contain? and by how much? 

Specifically, here we would be examining the nutritional information on Starbucks 
drinks. We will first ask ourselves two questions about the nutrition of Starbucks 
drinks and explore these questions individually using the dataset. The dataset 
has been collected from the *Starbucks Coffee Company* Beverage Nutrition 
Information. The dataset includes the product name, size of drinks (name & mL) 
and nutrition facts about the drinks which includes:

* Amount of calories
* Level of fat (total, saturated & trans),
* Cholesterol, 
* Carbohydrates
* Fiber
* Sugars
* Sodium
* Caffeine

The one major limitation from this dataset is that this is the expected 
nutrition of the drinks, which means that there might be a difference
in the nutrition content of the drinks we actually order compared to the ones 
listed in this dataset. We are unsure on the significance of this difference.





















Questions & Rationale
===================================== 



Row 
------------------------------------
### **Research Questions**

> **`r text_spec("Q1: How do Starbucks beverages vary in calories and key nutrients?", color = "red")`**

**`r text_spec("Learning Outcome", color = "red")`** &nbsp;  
Understand the range and variability of nutritional content in Starbuck drinks. 
Identify specific drinks and types of drinks with notable nutrient profiles. 
This learning outcome is achieved by answering the subquestions listed here:

&nbsp;  

*`r text_spec("What is the distribution of calories in Starbucks drinks?", color = "red")`* &nbsp;  
Use the calories data of each drink to plot a histogram of calories of Starbuck 
drinks.  

*`r text_spec("How do the nutrition levels vary in these drinks?", color = "red")`* &nbsp;  
Take all the nutrition facts data and create a summary for each of these nutrition 
components. The summary should display the mean, median, minimum, maximum, 
standard deviation, 25th quartile and 75th quartile of each nutrition component. 

*`r text_spec("How does nutrition vary between Starbucks drink size?", color = "red")`* &nbsp;  
Take all the nutrition facts data and create a boxplot (using the size data as 
our explanatory variable) for each of these nutrition components.

*`r text_spec("What is the relationship between the amount of calories and the nutritional content in the drinks?", color = "red")`* &nbsp;  
Create a multivariate linear regression model which captures the effects of the 
other nutrition components on calories. 

*`r text_spec("Are there specific types of drinks that stand out in terms of being lower or higher in calories?", color = "red")`* &nbsp;  
Sort the data according to the amount of calories of each and the find the 
highest and lowest 10 drinks.

&nbsp;


***


> **`r text_spec("Q2: How does the choice of milk and whipped cream affect nutritional content of drinks?", color = "red")`**

**`r text_spec("Learning Outcome", color = "red")`** &nbsp;  
Explore the impact of diverse milk types on the nutritional composition of 
Starbucks drinks. Identify whether certain milk alternatives contribute to 
healthier options. Understand the influence of whip cream on the overall 
nutritional profile of drinks. This learning outcome is achieved by answering 
the subquestions listed here:  

&nbsp;

*`r text_spec("How does the presence of whip cream impact the calorie content and other nutritional components?", color = "red")`* &nbsp;  
Take all the nutrition facts data and create a boxplot (using the whip data as 
our explanatory variable) for each of these nutrition components. Also use the
calorie data and whip data to create a bivariate linear regression model.

*`r text_spec("Which types of milk are associated with lower calorie and healthier options?", color = "red")`* &nbsp;  
Create a multivariate linear regression model which captures the effects of the 
milk types on calories. The variables in this model are dummy variables and 
hence we will have to elect "no milk" to be the base category and exclude it 
from the model to avoid perfect multicollinearity. 

*`r text_spec("How do different types of milk impact the nutritional content of Starbucks drinks?", color = "red")`* &nbsp;  
Take all the nutrition facts data and create a boxplot (using the milk data as 
our explanatory variable) for each of these nutrition components.

&nbsp;



```{r read-data, message=FALSE}
raw_starbucks <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-12-21/starbucks.csv')
```



Row 
------------------------------------

### **Missing Values** &nbsp;  
Before we start to analyse our data, we will need to examine and clean up any 
missing values in our raw dataset.Here we find that there are `r raw_starbucks |> n_miss()` 
missing values within the dataset, so we do not need to clean up for missing values.



Row 
------------------------------------  

### **Data Description**  &nbsp;  
The dataset contains `r nrow(raw_starbucks)` observations and `r ncol(raw_starbucks)` 
variables. The dataset contains the Starbuck drink name; drink size; milk type 
used; whether or not whipped cream was added or not; and nutrition fact. 
Nutrition fact includes:

* Calories (KCal)
* Total Fat (g)
* Saturated Fat (g)
* Trans Fat (g)
* Cholesterol (mg)
* Sodium (mg)
* Total Carbs (g)
* Fiber (g)
* Sugar (g)
* Caffeine (mg)

There are `r n_distinct(raw_starbucks$product_name)` Starbuck drinks in this 
dataset. The values of the `whip` variable are encoded in binary 0 and 1 to 
represent whip not added and whip added to the drink, respectively. Additionally, 
the values `milk` variable are encoded from 0 to 5 to represent the milk type 
added into the drink. 



Row 
------------------------------------  

### **Data Cleaning**  &nbsp;  
Most of the data types are already formatted correctly. However variables 
`trans_fat_g` and `fiber_g` are character types, when they should instead be
formatted as numeric types. Therefore, we will have to convert `trans_fat_g` and 
`fiber_g` into numerics. The `whip` variable is a binary variable binary which 
means that its values are either 0 or 1, so we should change its type from 
character to logical. 

```{r type-cleaning, message=FALSE}
type_starbucks <- raw_starbucks |> mutate(trans_fat_g = as.numeric(trans_fat_g)) |> 
                                      mutate(fiber_g = as.numeric(fiber_g)) |> 
                                        mutate(whip = as.logical(whip))
```

An examination of the sizes of the Starbucks drinks shows that it includes the 
number of shots added to the drinks (e.g., solo, doppio, triple, etc.). 

``` {r echo=FALSE}
unique(raw_starbucks$size)
```

We are not interested in the number of expresso shots added into the drinks 
because we are mainly interested in the actual sizes (i.e., short, tall, grande, 
venti & trenta) of the drinks. So we will remove observations containing the 
sizes solo, doppio, triple, quad, 1 scoop, 1 shot from our dataset. After this, 
we can transform the sizes into the factor type and order them accordingly via the
level property of the factor type.

``` {r remove-size}
size_level <- c("short", "tall", "grande", "venti", "trenta")

updated_size_starbucks <- type_starbucks |> filter(size %in% c("short","tall","grande","venti","trenta")) |> 
                              mutate(size = factor(size, levels=size_level))
```

The `milk` variable is currently a double type and its values ranges from 1-5 
where each number represents a milk type:

* 0 = No milk
* 1 = No fat
* 2 = 2% milk (reduced-fat milk)
* 3 = Soy milk
* 4 = Coconut milk
* 5 = Whole milk (regular milk)

Therefore we will perform a mapping from these numeric values to these characters. 
After that, we turn `milk` from a character to a factor type and order them 
accordingly via the level property of the factor type such that "no milk" is 
first in the level. We decode the number 0-5, so that our analysis will be easier
down the line. Hence, we have cleaned our dataset and are now ready to explore and 
model our data. 

``` {r milk-type}
milk_level <- c("no_milk","nonfat","2%_fat","soy","coconut","whole")

milk_typ_starbucks <- updated_size_starbucks |> mutate(milk = case_when(
  milk == 0 ~ "no_milk",
  milk == 1 ~ "nonfat",
  milk == 2 ~ "2%_fat",
  milk == 3 ~ "soy",
  milk == 4 ~ "coconut",
  milk == 5 ~ "whole",
  )) |> mutate(milk = factor(milk, level=milk_level))

size_level <- c("short", "tall", "grande", "venti", "trenta")

clean_starbucks <- milk_typ_starbucks
```




















Question 1
===================================== 




Row
------------------------------------
###  **Distribution of Calories of Starbucks Drinks**
```{r distribution-cal}
distribution_cal <- clean_starbucks |> ggplot(aes(x=calories)) +
                    geom_histogram(binwidth=25, colour="black", fill="white") +
                    geom_vline(aes(xintercept=mean(calories)), color="red", size=1) + 
                    scale_x_continuous(
                      breaks = seq(min(clean_starbucks$calories), 
                                   max(clean_starbucks$calories), by=100
                                   )) +
                    labs(
                      y = "Number of Drinks",
                      x = "Calories (kCal)"
                    )

ggplotly(distribution_cal)
```




Row {.tabset .tabset-fade}
------------------------------------
 **Nutrition Statistics**
```{r stat-satfat}
summarise_nutrition <- function(data, variable) {
  sum_nutrition <- data %>%
    summarise(
      Mean = mean({{ variable }}),
      Median = median({{ variable }}),
      Minimum = min({{ variable }}),
      Maximum = max({{ variable }}),
      `Std Dev` = sd({{ variable }}),
      `Quartile 1` = quantile({{ variable }}, probs = 0.25),
      `Quartile 3` = quantile({{ variable }}, probs = 0.75)
    )
  
  sum_nutrition <- t(sum_nutrition)
  
  kable(sum_nutrition) |> kable_styling(full_width = FALSE) 
}
```
### **Calories (kCal)**
```{r}
summarise_nutrition(clean_starbucks, calories)
```

### **Total Fat (g)**
```{r}
summarise_nutrition(clean_starbucks, total_fat_g)
```

### **Trans Fat  (g)**
```{r}
summarise_nutrition(clean_starbucks, trans_fat_g)
```

### **Saturated Fat (g)**
```{r}
summarise_nutrition(clean_starbucks, saturated_fat_g)
```

### **Cholesterol (mg)**
```{r}
summarise_nutrition(clean_starbucks, cholesterol_mg)
```

### **Sodium (mg)**
```{r}
summarise_nutrition(clean_starbucks, sodium_mg)
```

### **Carbohydrates (g)**
```{r}
summarise_nutrition(clean_starbucks, total_carbs_g)
```

### **Fiber (g)**
```{r}
summarise_nutrition(clean_starbucks, fiber_g)
```

### **Sugar (g)**
```{r}
summarise_nutrition(clean_starbucks, sugar_g)
```

### **Caffeine (mg)**
```{r}
summarise_nutrition(clean_starbucks, caffeine_mg)
```



Row {.tabset .tabset-fade}
------------------------------------
 **Comparison of the Amount of Nutrients in Different Drink Sizes**
```{r rel-drinknut}
boxplot_nutrition <- function(data, variable, y_name){
  bplot <- ggplot(data, aes(x = size, y = {{ variable }}, fill = size)) +
    geom_boxplot(alpha = 0.3) +
    theme(legend.position = "none") +
    scale_fill_brewer(palette = "Pastel2") +
    labs(
      x = "Size Type",
      y = y_name
    )
  
  ggplotly(bplot)
}
```

### **Calories (kCal)**
```{r}
boxplot_nutrition(clean_starbucks, calories, "Calories (kCal)")
```

### **Total Fat (g)**
```{r}
boxplot_nutrition(clean_starbucks, total_fat_g, "Total Fat (g)")
```

### **Trans Fat (g)**
```{r}
boxplot_nutrition(clean_starbucks, trans_fat_g, "Trans Fat (g)")
```

### **Saturated Fat (g)**
```{r}
boxplot_nutrition(clean_starbucks, saturated_fat_g, "Saturated Fat (g)")
```

### **Cholesterol (mg)**
```{r}
boxplot_nutrition(clean_starbucks, cholesterol_mg, "Cholesterol (mg)")
```

### **Sodium (mg)**
```{r}
boxplot_nutrition(clean_starbucks, sodium_mg, "Sodium (mg)")
```

### **Carbohydrates (g)**
```{r}
boxplot_nutrition(clean_starbucks, total_carbs_g, "Total Carbs (g)")
```

### **Fiber (g)**
```{r}
boxplot_nutrition(clean_starbucks, fiber_g, "Fiber (g)")
```

### **Sugar (g)**
```{r}
boxplot_nutrition(clean_starbucks, sugar_g, "Sugar (g)")
```

### **Caffeine (mg)**
```{r}
boxplot_nutrition(clean_starbucks, caffeine_mg, "Caffine (mg)")
```



Row
------------------------------------
### **The Effect of Other Nutrition Content and Serve Size on Calories**
```{r}
lm(calories ~ serv_size_m_l + total_fat_g + cholesterol_mg + sodium_mg + total_carbs_g, data = clean_starbucks) |> summary()
```
The model is represented as
$$\widehat{Calories} = 9.377 + \underset{0.0004}{0.0133}\text{ ServeSize} + 
\underset{0.188}{9.016}\text{ TotalFat} + \underset{0.059}{0.337}\text{ Cholesterol}
+ \underset{0.010}{0.074}\text{ Sodium} + \underset{0.046}{3.756}\text{ Carbs} \\
n=1116, \enspace R^2=0.9832$$



Row {.tabset .tabset-fade}
------------------------------------

```{r mean-cal}
mean_cal <- clean_starbucks |> 
                    group_by(product_name) |> 
                      summarise(avg_cal = mean(calories)) |> 
                        arrange(desc(avg_cal))
```

### **Top 10 Drinks with the Highest Calories**
```{r}
head(mean_cal, 10) |> rename(`Average Calories (kCal)` = avg_cal, `Product Name` = product_name) |> 
  kable() |> 
    kable_styling(bootstrap_options = c("hover", "striped"))
```

### **Top 10 Drinks with the Lowest Calories**
```{r}
tail(mean_cal, 10) |> rename(`Average Calories (kCal)` = avg_cal, `Product Name` = product_name) |> 
  kable() |> 
    kable_styling(bootstrap_options = c("hover", "striped"))
```



Column {.sidebar data-width=400}
----
> **Distribution of Calories**

* The distribution of calories in Starbucks drinks are positively skewed
* Most of the drinks lie within the 150-300 calorie range


***


> **Nutrition Statistics**

* The average amount of calories is 234kCal and the median is 220kCal, so 
the average amount is not far off from the median.
* The drink with the highest calorie count contains 640kCal, whereas the drink
with the lowest calorie count contains no calories.
* The IQR of calories is between 140 to 320kCal.
* The average amount of cholesterol is 15.6g, the median is 5g and the highest 
cholesterol amount is 75g.
* The mean and median sodium in a drink are not too far from each other at 143mg
and 135mg respectively.
* The average amount of fiber in a drink is 0.89g and the IQR is between 0 to 1g.
* The average drink contains 36g of sugar and the IQR is between 19 to 49g.
* The average drink contains 89.7mg of caffeine and the drink with the highest.
amount of caffeine contains 475mg.


***


> **Nutrition Variation in Drink Sizes**

* Trenta is the largest serve size that Starbuck offers, however, most of the
drinks available in trenta size surprisingly have less calories and other 
nutrition components compared to grande (third largest size) and venti (
second largest size). 
* There is an outlier in the calories of a drink in trenta size; 
one of the drinks have an extremely low calorie amount at 5 kCal.
* In general, as the serve size becomes larger, the amount of nutrition
components also increase (except for trenta).
* In general, venti serve size has the largest amount of nutrition
and either short or trenta serve size contains the least amount of nutrition.
* The reason trenta may not align with expectations is that this serve size is
only served for cold drinks.


***


> **Calorie Model**

* 98.32% of the sample variation of calories in Starbuck drinks can be explained
by the variation in serve size in millilitres, amount of total fat, cholesterol,
sodium and carbohydrates.
* Fat and carbohydrates are predicted to have a significant effect on the average .
amount of calories in Starbuck drinks while holding other nutrition components
constant.
* The serve size is predicted to have an insignificant effect on the average
amount of calories in Starbuck drinks.
* All regressors are individually significant at the 1% significance level.
* Variables such as saturated fat, trans fat, fiber and sugar have been excluded
from the model to avoid near multicollinearity (as these nutrition components
relate to either total fat or carbohydrates).


***


> **High and Low Calorie Drinks**

* The drinks with the highest calorie count tend to have some form of
confectionary product within them (e.g., chocolate, caramel, vanilla).
* Most of these high calories drinks are either mocha or frappuccino.
* The drinks with the lowest calories count are a variation of brewed tea.




















Question 2
===================================== 




Row
------------------------------------
### **Summary Statistics for Milk**
```{r}
total_whip <- clean_starbucks |> filter(whip == TRUE) |> nrow()
total_drinks <- clean_starbucks |> nrow()
```

```{r}
clean_starbucks |> 
  group_by(milk) |> 
  summarise(
    Number = n(),
    Proportion = percent(n()/total_drinks, accuracy = 0.1)
  ) |> 
  mutate(milk = case_when(
    milk == "nonfat" ~ "Non Fat",
    milk == "2%_fat" ~ "2% Fat",
    milk == "coconut" ~ "Coconut",
    milk == "soy" ~ "Soy",
    milk == "whole" ~ "Whole",
    milk == "no_milk" ~ "No Milk",
  )) |> 
  rename(`Milk Type` = milk) |> 
  arrange(desc(Number)) |> 
  kable() |> 
    kable_styling(bootstrap_options = c("hover", "striped")) 
```



Row {.tabset .tabset-fade}
------------------------------------
**Nutrition in Whip and Non-whip Drinks**
```{r}
whip_nutrition <- function(data, variable, y_name){
  data$whip_label <- ifelse(data$whip, "Whipped", "Not Whipped")

  bplot <- ggplot(data, aes(
    x = whip_label,
    y = {{ variable }},
    fill = whip_label
  )) +
    geom_boxplot(alpha = 0.3) +
    theme(legend.position = "none") +
    labs(
      x = "",
      y = y_name
    )

  ggplotly(bplot)
}
```
### **Calories (kCal)**
```{r}
whip_nutrition(clean_starbucks, calories, "Calories (kCal)")
```

### **Trans Fat (g)**
```{r}
whip_nutrition(clean_starbucks, trans_fat_g, "Trans Fat (g)")
```

### **Saturated Fat (g)**
```{r}
whip_nutrition(clean_starbucks, saturated_fat_g, "Saturated Fat (g)")
```

### **Cholesterol (mg)**
```{r}
whip_nutrition(clean_starbucks, cholesterol_mg, "Cholesterol (mg)")
```

### **Sodium (mg)**
```{r}
whip_nutrition(clean_starbucks, sodium_mg, "Sodium (mg)")
```

### **Carbohydrates (g)**
```{r}
whip_nutrition(clean_starbucks, total_carbs_g, "Total Carbs (g)")
```

### **Fiber (g)**
```{r}
whip_nutrition(clean_starbucks, fiber_g, "Fiber (g)")
```

### **Sugar (g)**
```{r}
whip_nutrition(clean_starbucks, sugar_g, "Sugar (g)")
```



Row 
------------------------------------
### **The Effect of Whip Cream on Calorie Content**
```{r}
lm (calories ~ whip, data=clean_starbucks) |> summary()
```
The model is represented as:
$$ \widehat{Calories} = 188.53 + \underset{7.57}{182.69}\text{Whip} \\ n = 1116, R^2 = 0.3436$$
where whip is a dummy variable which represents the presence of whip cream (whip=1)
or not (whip=0).



Row 
------------------------------------
### **The Effect of Milk Type on Calorie Content**
```{r}
lm (calories ~ milk, data=clean_starbucks) |> summary()
```

The model is represented as:
$$ \widehat{Calories} = 74.40 + \underset{12.32}{74.4}\text{NonFat} + 
\underset{12.75}{115.17}\text{TwoPercentFat} + \underset{12.75}{201.95}\text{Soy} + 
 \underset{12.75}{171.95}\text{Coconut} + \underset{12.75}{223.51}\text{Whole} 
 \\ n = 1116, R^2 = 0.2521$$
The variables listed here are dummy variables and the base category is "no milk". 
The variable "no milk" is not included to avoid the dummy variable trap.



Row {.tabset .tabset-fade}
------------------------------------
**Nutritional Content in Different Milk Types**
```{r }
milk_nutrition = function(data, variable, y_name){
  bplot <- 
    data |>
      mutate(milk = case_when(
        milk == "nonfat" ~ "Non Fat",
        milk == "2%_fat" ~ "2% Fat",
        milk == "coconut" ~ "Coconut",
        milk == "soy" ~ "Soy",
        milk == "whole" ~ "Whole",
        milk == "no_milk" ~ "No Milk",)) |> 
    
          ggplot(aes(x = milk, y = {{ variable }}, fill=milk)) +
          geom_boxplot(alpha = 0.3) +
                    theme(legend.position = "none") +
          scale_fill_brewer(palette = "Pastel2") +
          labs(
            x = "Milk Type",
            y = y_name
          )
  
  ggplotly(bplot)
}
```
### **Calories (kCal)**
```{r}
milk_nutrition(clean_starbucks, calories, "Calories (kCal)")
```

### **Total Fat (g)**
```{r}
milk_nutrition(clean_starbucks, total_fat_g, "Total Fat (g)")
```

### **Trans Fat (g)**
```{r}
milk_nutrition(clean_starbucks, trans_fat_g, "Trans Fat (g)")
```

### **Saturated Fat (g)**
```{r}
milk_nutrition(clean_starbucks, saturated_fat_g, "Saturated Fat (g)")
```

### **Cholesterol (mg)**
```{r}
milk_nutrition(clean_starbucks, cholesterol_mg, "Cholesterol (mg)")
```

### **Sodium (mg)**
```{r}
milk_nutrition(clean_starbucks, sodium_mg, "Sodium (mg)")
```

### **Carbohydrates (g)**
```{r}
milk_nutrition(clean_starbucks, total_carbs_g, "Total Carbs (g)")
```

### **Fiber (g)**
```{r}
milk_nutrition(clean_starbucks, fiber_g, "Fiber (g)")
```

### **Sugar (g)**
```{r}
milk_nutrition(clean_starbucks, sugar_g, "Sugar (g)")
```

### **Caffeine (mg)**
```{r}
milk_nutrition(clean_starbucks, caffeine_mg, "Caffine (mg)")
```



Column {.sidebar data-width=400}
----
> **Impact of Whip Cream**

* The proportion of drinks with whip cream is `r total_whip/total_drinks`.
* The boxplots shows us that the presence of whip cream generally increases the 
amount of nutrition content in the drink.
* In the model, the presence of whip cream is predicted to increase the amount
of calories in a drink by 183kCal on average compared to a drink without whip
cream.
* The regressor whip cream is significant at the 5% significance level.


***


> **Milk Model**

* In the summary statistics, non fat milk appears to be the most common milk 
type, whereas no milk is the least common milk type
* In the model, it is predicted that a drink with no milk has 74.4 kCal on average.
The other milk choices unsurprisingly increases the amount of calories in the
drink.
* Whole milk is predicted to have the largest increase in calories compared to the
other milk types. It is predicted that a drink with whole milk has 297.91 kCal 
on average. This is roughly four times larger in calorie amount compared to no milk.
* Unsurprisingly, nonfat milk is predicted to have a less pronounced effect on 
calorie amount compared to 2% fat milk on average.
* Soy milk and coconut milk are predicted to have a more pronounced effect on 
calorie amount compared to the low-fat milk types.


***


> **Nutrition Content in Different Types of Milk**

* The no milk type has some outliers with very high calorie count, which are
larger than the median calorie amount of other milk types; these outliers have
a calorie amount between 360-450kCal
* Unsurprisingly, non fat milk has less total fat compared to 2% fat milk. However,
there is an outlier in one of the non fat milk which contains 20g of total fat.
This may be due to some other ingredient added into the drink. 
* Whole milk generally has higher cholesterol compared to the other milk options.
Whole milk has an IQR of 15-45g of cholesterol.
* The IQR and median of sodium, carbohydrates, fiber and sugar are similar
in terms of milk types that are not "no milk" possess similar medians and IQR, and
no milk tends to be lower compared to the rest. This may be due to the fact
that fiber and sugar fall under carbohydrates, so they will exhibit a similar 
pattern. 
* The choice of milk types do not lead to a significant change in the amount of 
fiber taken.
* Surprisingly, no milk types contains some outliers with a high amount of caffeine 
(roughly 380-475mg).










Conclusion & References
===================================== 



Row 
------------------------------------
### **Conclusion**

**Q1 - Variation in Calories and Key Nutrients in Starbuck Drinks** &nbsp;  

In the analysis, it was found that drinks with larger serve size generally have
higher amounts of calories and key nutrients compared to smaller serve sizes. 
This was expected, however, the largest serve size, trenta, did not follow this 
pattern. This may be due to the types of drinks that are not available in trenta
size. Additionally, drinks that contained confectionary products (e.g., chocolate,
caramel) were found to have a high amounts of calories, whereas brewed teas contained
no calories at all. 

The distribution of calories are positively skewed and it was found that the middle
50% of calories of drinks lie between 140-320. According to the Washington State
Department of Social and Health Services (n.d.), 140-320 calories is considered to
be a moderate amount. The average amount of cholesterol is 15.6g which is around
1/20th of the maximum amount recommended per day (UCSF Health, 2023). The average
amount of sodium is 143mg and that is an adequate amount considering that adults
need between 460-920mg of sodium per day to function (Reading Food Nutrition Labels, 
n.d.). The average drink contains 36g of sugar, which is already more than half of 
the recommended limit (Health Direct, n.d.). Furthermore, the average drink 
contains 89.7mg of caffeine which covers 22.5% of the recommended limit of caffeine
intake (FDA, n.d.).

The model created shows that drinks high in fat and carbohydrates generally have a 
higher calorie count compared to drinks low in fat and carbohydrates. 

Therefore, if a person wants to buy a drink from Starbucks and they are health 
conscious, it is recommended for them to buy a maximum of one drink for themselves
and the drink should be a variation of tea. 


***


**Q2 - Whip Cream and Milk** &nbsp;  

In the two models built, it was found that drinks with whip cream significantly
contained a higher calorie amount compared to drinks without cream. It was predicted
that on average, a drink with whip cream added would have an additional 183kCal
compared to drinks without whip cream.

Furthermore, the model built for examining the effects of different milk types
on calorie showed that no milk type resulted in drinks with low calorie amount, 
whereas whole milk type resulted in drinks with high calorie amount. It was
predicted that whole milk increases the calorie amount by 224kCal compared to 
drinks with no milk. 

Additionally, some key nutrients such as carbohydrates, sodium, fiber and sugar
were not significantly affected by the milk type, other than the "no milk", in which
case, it would result in less key nutrients. However, milk type does have an affect
on the intake of total fat and cholesterol with whole milk generally increasing
the amount of these key nutrients. 

Therefore, if a person wants to buy a drink from Starbucks and they are health
conscious, it is recommended for them to buy a drink with no milk and no whip
cream. 



Row 
------------------------------------
### **References** &nbsp;  

FDA. (n.d.). Retrieved from https://www.fda.gov/consumers/consumer-updates/spilling-beans-how-much-caffeine-too-much#. &nbsp;  

Health Direct. (n.d.). Retrieved from https://www.healthdirect.gov.au/sugar#. &nbsp;  

Reading Food Nutrition Labels. (n.d.). Retrieved from https://www.dshs.wa.gov/sites/default/files/ALTSA/stakeholders/documents/duals/toolkit/Reading%20Food%20Nutrition%20Labels.pdf &nbsp;  

Salt and sodium (N.d.). Retrieved from https://www.healthdirect.gov.au/salt &nbsp;  

UCSF Health. (2023). Retrieved from https://www.ucsfhealth.org/education/cholesterol-content-of-foods#. &nbsp;  

[datasetsource]: https://github.com/rfordatascience/tidytuesday/tree/master